---
title: "Design v2"
format: html
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
here::i_am("dev/design2.qmd")
library(here)
```

# Planning

### Design All: design_*

`design_ct`

- `study_type`: "chest", "whole_abd", "chest_whole_abd", "cta_liver"

### Design Study

-   CT Chest: `design_chest`
-   CT Whole abdomen: `design_whole_abd`
-   CT Chest + Whole abdomen: `design_chest_whole_abd`
-   CTA liver: `design_cta_liver`

Template

{study_type}
Body weight: `weight_kg` kg 
kV: `kV` 
mA: auto 
Noise index: `noise_index` 
Delay: ___ sec 
`print_contrast()`
`print_rate_ml_sec()`

# Design All

```{r design_ct}
design_ct <- function(study_type,
                      age_group,
                      weight_kg,
                      rate_formula = c("no_delay", "delay"),
                      delay_sec = NULL) {
  
  study_type <- match.arg(study_type, 
                          choices = c("chest", "whole_abd",
                                      "chest_whole_abd", "cta_liver"))
  age_group <- match.arg(age_group, 
                         choices = c("younger_child", "older_child"))
  rate_formula <- match.arg(rate_formula)
  
  # CT Chest
  if(study_type == "chest") {
    design_chest(age_group = age_group, weight_kg = weight_kg)
  }
  # CT Whole Abdomen
  if(study_type == "whole_abd") {
    design_whole_abd(age_group = age_group, weight_kg = weight_kg,
                     rate_formula = rate_formula, delay_sec = delay_sec)
  }
  # CT Chest + WA
  if(study_type == "chest_whole_abd") {
    design_chest_whole_abd(age_group = age_group, weight_kg = weight_kg,
                           rate_formula = rate_formula, delay_sec = delay_sec)
  }
  # CTA Liver
  if(study_type == "cta_liver") {
    design_cta_liver(age_group = age_group, weight_kg = weight_kg)
  }
}

design_ct("chest", "younger", 3)
design_ct("whole_abd", "older", 6, "delay", 65)
```

# Design Study

## CT Chest

```{r design_chest}
design_chest <- function(age_group,
                         weight_kg
                         ) {
  
    age_group <- match.arg(age_group, 
                           choices = c("younger_child", "older_child"))
    
    cat("-- Design CT --", "\n\n")
    cat("CT chest, venous only","\n")
    # Weight
    cat("Body weight:", weight_kg, "kg", "\n")
    
    # kV
    kV <- get_kV(weight_kg)
    cat("kV:", kV, "\n")
    # mA
    cat("mA: auto", "\n")
    # Noise
    noise_index <- switch (age_group,
      "younger_child" = 17,
      "older_child" = 20
    )
    cat("Noise index:", noise_index, "\n")
    # Delay
    cat("Delay: 45 sec", "\n")
    # Contrast
    ml_kg <-  1 # Chest
    print_contrast(ml_kg = ml_kg, weight_kg = weight_kg); cat("\n")
    # Rate
    print_rate_ml_sec(
      contrast_ml = get_contrast_ml(ml_kg = ml_kg, weight_kg = weight_kg), 
      rate_formula = "no_delay"
    )
    cat("\n\n---")
  
}

design_chest("younger_child", 12)
design_chest("older_child", 50)
```



## CT Whole abdomen

```{r design_whole_abd}
design_whole_abd <- function(age_group,
                             weight_kg, 
                             rate_formula = c("no_delay", "delay"),
                             delay_sec = NULL
                             ){
  
    age_group <- match.arg(age_group,
                           choices = c("younger_child", "older_child"))
    rate_formula <- match.arg(rate_formula)

    cat("-- Design CT --", "\n\n")
    cat("CT whole abdomen, venous only","\n")
    # Weight
    cat("Body weight:", weight_kg, "kg", "\n")

    # kV
    kV <- get_kV(weight_kg)
    cat("kV:", kV, "\n")
    # mA
    cat("mA: auto", "\n")
    # Noise
    noise_index <- switch (age_group,
      "younger_child" = 15,
      "older_child" = 17
    )
    cat("Noise index:", noise_index, "\n")
    # Delay
    if (rate_formula == "no_delay") {
      cat("Delay: 60 or 65 or 70 sec", "\n")
    } else {
      cat("Delay:", delay_sec, "\n")
    }
    
    # Contrast
    ml_kg <- 2 # WA
    print_contrast(ml_kg = ml_kg, weight_kg = weight_kg); cat("\n")
    # Rate
    print_rate_ml_sec(
      contrast_ml = get_contrast_ml(ml_kg = ml_kg, weight_kg = weight_kg),
      rate_formula = rate_formula,
      delay_sec = delay_sec
    )
    cat("\n\n---")
  
}

design_whole_abd("younger_child", 12)
design_whole_abd("younger_child", 12, "delay", 70)
```

## CT Chest + WA

```{r design_chest_whole_abd}
design_chest_whole_abd <- function(age_group,
                                   weight_kg, 
                                   rate_formula = c("no_delay", "delay"),
                                   delay_sec = NULL
                             ){
  
    age_group <- match.arg(age_group,
                           choices = c("younger_child", "older_child"))
    rate_formula <- match.arg(rate_formula)

    cat("-- Design CT --", "\n\n")
    cat("Venous chest + whole abdomen ","\n")
    # Weight
    cat("Body weight:", weight_kg, "kg", "\n")

    # kV
    kV <- get_kV(weight_kg)
    cat("kV:", kV, "\n")
    # mA
    cat("mA: auto", "\n")
    # Noise
    noise_index <- switch (age_group,
      "younger_child" = 15,
      "older_child" = 17
    )
    cat("Noise index:", noise_index, "\n")
    # Delay
    if (rate_formula == "no_delay") {
      cat("Delay: 60 or 65 or 70 sec", "\n")
    } else {
      cat("Delay:", delay_sec, "\n")
    }
    
    # Contrast
    ml_kg <- 2 # WA
    print_contrast(ml_kg = ml_kg, weight_kg = weight_kg); cat("\n")
    # Rate
    print_rate_ml_sec(
      contrast_ml = get_contrast_ml(ml_kg = ml_kg, weight_kg = weight_kg),
      rate_formula = rate_formula,
      delay_sec = delay_sec
    )
    cat("\n\n---")
  
}

design_chest_whole_abd("younger_child", 12)
```

## CTA Liver

```{r design_cta_liver}
design_cta_liver <- function(age_group,
                             weight_kg
                             ){
  
    age_group <- match.arg(age_group,
                           choices = c("younger_child", "older_child"))

    cat("-- Design CT --", "\n\n")
    cat("CTA liver","\n")
    # Weight
    cat("Body weight:", weight_kg, "kg", "\n")

    # kV
    kV <- get_kV(weight_kg)
    cat("kV:", kV, "\n")
    # mA
    cat("mA: auto", "\n")
    # Noise
    noise_index <- switch (age_group,
      "younger_child" = 15,
      "older_child" = 17
    )
    cat("Noise index:", noise_index, "\n")
    # Delay
    cat("Delay: 20 sec (CTA); 70 sec (Venous)", "\n")

    # Contrast
    ml_kg <- 2.5 # WA
    print_contrast(ml_kg = ml_kg, weight_kg = weight_kg); cat("\n")
    ml <- get_contrast_ml(ml_kg = ml_kg, weight_kg = weight_kg)
    
    # Rate
    rate <- (ml + 15) / 20
    rate_adj <- round_up_decimal(rate, 1) # Round up for 1 decimal
    cat(glue::glue("Rate: {rate_adj} ml/sec ({ml} + 15) / 20 = {round(rate, 3)}"))
    
    cat("\n\n---")
  
}

design_cta_liver("younger", 20.5)
```

